---
title: "childhood study"
author: "Alven"
date: "2021/2/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
library(stringr)
library(dplyr)
library(ggsci)
library(data.table)
library(ggthemes)
```

```{r}
## need not run
setwd("C:/Users/SURFACE/Desktop/paper google/修改稿-荣彬/r code")

## load data
```{r}
childhood <- read.csv(file = "Dataset 1.csv")
childhood$type <- as.factor(childhood$type)
childhood$State<-as.factor(childhood$State)
childhood$OverallRat<-as.factor(childhood$OverallRat)
```

## Choose the subset
```{r}
childhood_sub <- childhood[,c("X","type","State","OverallRat","main_50","main_100","main_300","main_500","main_1000","moto_50","moto_100","moto_300","moto_500","moto_1000")]


## reshape the data


childhood_sub_melt <- melt(childhood_sub,id.vars = c("X","type","State","OverallRat")) # change to long data
# set the classification to main/moto
childhood_sub_melt$class <- ifelse(childhood_sub_melt$variable %in% c("main_50","main_100","main_300","main_500","main_1000")==TRUE, 1, 0)
childhood_sub_melt$class <- factor(childhood_sub_melt$class,levels = c(0,1), labels = c("Motor","Main"))
# change the "variable" to "meters": stract numbers 
childhood_sub_melt$meters <- stringr::str_extract(childhood_sub_melt$variable,"[0-9]+")
childhood_sub_melt$meters <- factor(childhood_sub_melt$meters,levels = c("50","100","300","500","1000"))
``
#figure 5 from rongbin
data<-childhood_sub_melt
data<-filter(data,value>0)
data$value_level<-cut(data$value,breaks = c(-1,50,100,300,500,1000,20000),na.rm=TRUE)## chose a suitable breaks by yourself to make the figure beautiful
levels(data$value_level)
levels(data$value_level)<-c("(0,50]","(50,100]","(100,300]","(300,500]","(500,1000]",">1000")  ## relabel levels
levels(data$meter) 

levels(data$meter)<-c("50m buffer","100m buffer","300m buffer","500m buffer","1000m buffer")
data$State<-factor(data$State, levels=c("TAS","NT","ACT","SA","WA","QLD","VIC","NSW"))
figure_distance<-ggplot(data = data, 
       aes(x = State, fill = value_level ))+
        geom_bar(stat = "count") +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.background = element_rect(fill="transparent",color = "transparent"),
    axis.line = element_line(colour = "black"),
    legend.background = element_blank())+ 
  theme_classic(base_size = 20)+
  labs(x="State",y="Number of childcare centres ",fill="Length of road (m)")+scale_fill_lancet()+
   facet_grid(class ~meter)


figure_distance
ggsave("figure 5.png",width = 24, height = 9.77)


#figure 7 from rongbin
data$OverallRat<-factor(data$OverallRat,levels=c("SIR","EXT","WT","EXD","MT","NA"))
figure_distance<-ggplot(data = data, 
       aes(x = OverallRat, fill = value_level ))+
        geom_bar(stat = "count") +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.background = element_blank())+
  theme_classic(base_size = 20)+
  labs(x="Overall rate",y="Number. of childcare centres ",fill="Length of road (m)")+scale_fill_lancet()+
   facet_grid(class ~meter)

figure_distance
ggsave("figure 7.png",width = 24, height = 9.77)



#figure 9 from rongbin
data$type<-factor(data$type,levels=c("1","5","2","3","6","8","7","4"))
figure_distance<-ggplot(data = data, 
       aes(x = type, fill = value_level ))+
        geom_bar(stat = "count") +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.background = element_blank())+ labs(x="Type",y="Number. of childcare centres ",fill="Length of road (m)")+scale_fill_lancet()+
  theme_classic(base_size = 20)+
   facet_grid(class ~meter)

figure_distance
ggsave("figure 9.png",width = 24, height = 9.77)




